Solution of Differential Algebraic Equations with Manifold Constraints on the Latent Space of an Autoencoder

### 2019-05-15 paper/paper.tex
added in bibliography

@@

@@

The system of equations we are looking at are, for only two components,
\begin{align}
  \partial_t \rho_{H_2O} =& \nabla \cdot flux_{H_2O} + s \\
  \partial_t \rho_{CO_2} =& \nabla \cdot flux_{CO_2} + s \\
  \partial_t e& = \nabla \cdot flux_{heat} + s
\end{align}
More species add more rows, and applicaitons also involve continuum
mechanics and chemical reactions! The interplay of deformations,
reactions, and phase transitions makes the equations extremely difficult
to solve. \cite{my millstone paper}

@@

@@

Solve for \(q_1(t)\) and \(q_2(t)\) such that:

@@

\textbf{Only training the material representation, not the balance
laws.}

@@

The autoencoder parameterizes the constraint :

@@

@@

>>>>

\usepackage{chemmacros}
\usepackage{natbib}
\usepackage{lineno}

@@

% Patch equations to properly generate line numbers for review
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
  \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
  \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
  \renewenvironment{#1}%
     {\linenomath\csname old#1\endcsname}%
     {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
  \patchAmsMathEnvironmentForLineno{#1}%
  \patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

The system of equations we are looking at are, for only two components,
\begin{align}
  \partial_t \rho_{H_2O} =& \nabla \cdot flux_{H_2O} + s \\
  \partial_t \rho_{CO_2} =& \nabla \cdot flux_{CO_2} + s \\
  \partial_t e& = \nabla \cdot flux_{heat} + s
\end{align}
More species add more rows, and applicaitons also involve continuum
mechanics and chemical reactions! The interplay of deformations,
reactions, and phase transitions makes the equations extremely difficult
to solve. \cite{queiruga2018millstone}

@@

 \cite{wu_physics-informed_2018}
\cite{xie_tempogan:_2018}

@@

With the trained model, we solve for \(q_1(t)\) and \(q_2(t)\) such that:

@@

Only training the material representation, not the balance
laws.

@@

The decoder part of the network is inserted into the balance law

@@

Technique ssuch as L1 regularization would be needed to search for low
cost models that also satisfy our desire for Occam's razor
simplifications. (The IAPWS relations used a prelimary form of this
type of simplification, but are not optimal in the author's opinion.)

@@

\bibliographystyle{plainnat}
\bibliography{zotero}
